\vspace{-1.5cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2015-09-01 write_up/cricket.tex
Added Rank to Cricket

\begin{figure}[htbp]
\centering
\caption{Proportion of Matches Won Minus Matches Lost After Winning the Toss}
\includegraphics[scale=.85]{../figs/winbyType.pdf}
\label{fig:summary}
\end{figure}

\begin{figure}[htbp]
\centering
\caption{Proportion of Matches Won Minus Matches Lost After Winning the Toss}
\includegraphics[scale=.85]{../figs/winbyDayNight.pdf}
\label{fig:summary}
\end{figure}

\begin{figure}[htbp]
\centering
\caption{Proportion of Matches Won Minus Matches Lost After Winning the Toss}
\includegraphics[scale=.85]{../figs/winbyDL.pdf}
\label{fig:summary}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\caption{Percentage of Matches Won Minus Matches Lost After Winning the Toss by Type of Match}
\includegraphics[scale=.85]{../figs/winbyType.pdf}
\label{fig:summary}
\end{figure}

\begin{figure}[htbp]
\centering
\caption{Percentage of Matches Won Minus Matches Lost After Winning the Toss By Day/Night}
\includegraphics[scale=.85]{../figs/winbyDayNight.pdf}
\label{fig:summary}
\end{figure}

\begin{figure}[htbp]
\centering
\caption{Percentage of Matches Won Minus Matches Lost After Winning the Toss by Duckworth Lewis}
\includegraphics[scale=.85]{../figs/winbyDL.pdf}
\label{fig:summary}
\end{figure}

\begin{figure}[htbp]
\centering
\caption{Percentage of Matches Won Minus Matches Lost After Winning the Toss by Difference in Ranks}
\includegraphics[scale=.85]{../figs/winbyRank.pdf}
\label{fig:summary}
\end{figure}
